%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    { DevOps Engineer } % Job title
    {Retraced GmbH} % Organization
    {Germany} % Location
    {May. 2023 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead DevOps team - own all Cloud Operations, CI/CD, Infrastructure-As-Code workflows and all things automation}
        \item {Desinged and built Self Service - developers can spin up a microservice under 10 minutes with a single-click  from what used to take more than 3 hours.}
        \item {Led and executed the project to make organization ISO27001 compliant for 2 consecutive years - from drafting organizational structures to enforcing Controls}
        \item {Single Click Disaster Recovery - spins up the frontend on Cloudflare, Kubernetes Cluster and Database. }
        \item {Optimized datadog usage and brough down costs by 30percent }
        \item {Owned all things security - managing the penetration testing and mitigaing all vulnerabilities and Continuously enhancing security.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{1\baselineskip}
  \cventry
    { Lead DevOps Engineer } % Job title
    {Infosys} % Organization
    {Hyderabad, India} % Location
    {Nov.2020 - April 2023 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead the project in transforming into Microservices on Openshift leveraging helm charts and Argo CD.}
        \item {Provided technical leadership and mentorship to DevOps engineers, guiding them in applying best practices and selecting the right tools for diverse project requirements. }
        \item {Managed multiple Cloud operations - from automating building CIS compliant images for a banking client to Terraforming entire stack on AWS and Azure. }
        \item {Designed scalable CI/CD pipelines and configuration management frameworks for microservices on Kubernetes with Azure DevOps and GitHub Actions}
        \item {Built Automation pipelines for data migration on Informatica Intellign Cloud System leveraging Azure DevOps pipeliens and RedGate tools.}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{1\baselineskip}
  \cventry
    { Site Reliability Engineer } % Job title
    {Axelerant} % Organization
    {Hyderabad, India} % Location
    {Jan.2020 - Oct. 2020 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and implemented the AWS cloud infrastructure to facilitate a seamless on-premise to cloud migration. } 
        \item {Designed and built repeatable multi-cloud Infrastructure as code templates leveraging Terraform and GitlabCI}
        \item {Led the project to migrate a monolith on-premise application to microservics on Cloud - from Dockerizing to helmizing the entire project. }
        \item {Created Branch based deployments leveraging namespaces in Kubernetes and GitLabCI Environments}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{1\baselineskip}
  \cventry
    { Site Reliability Engineer } % Job title
    {Cognizant} % Organization
    {Hyderabad, India} % Location
    {Jan.2019 - Dec 2019 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and build Deployment workflows for Machine Learning Modules on GitHub Actions}
        \item {Develop helm charts to deploy the instance of an application in any Kubernetes cluster. }
        \item { Played a key role in migrating application from Rancher (cattle) to Kubernetes }
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{1\baselineskip}
  \cventry
    { DevOps Engineer } % Job title
    {Deloitte} % Organization
    {Hyderabad, India} % Location
    {Jul.2010 -  Nov 2018 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the project for Cloud adoption migrating on-prem applications on Azure.}
        \item {Developed Ansible playbooks to deploy monitoring agent across 100s of VMs.}
        \item {Designed and built CI/CD pipelines for Java and .NET applications on Jenkins and Azure DevOps}   
        \item {Automated reporting and Certificate renewal using Python.}
        \item {Mentored colleagues on Linux, Docker, and Ansible}
      \end{cvitems}
    }

\end{cventries}
